\thetitle

### 2010-01-22 doc/paper.tex
doc: Make grammar work with hidden todo's; add note about DN rationale.
Ignore-this: e77bee7f267bcef4ae01532a943f2b54

darcs-hash:20100122114551-bab43-549fcb4983f7aaedfa14528684d666cebd99ee0c.gz

The prototype implementation described in \cite{alur} was developed in \todo{some ordinary programming language}, using \todo{some ordinary programming libraries}. The potential for bugs and floating point artifacts inherent in this approach limit the confidence one can justifiably have in safety judgements made by such an implementation. In this report, we describe a reimplementation of the basic technique in Coq, a proof assistant based on a rich type theory that also functions as a programming language, letting one develop ``certified'' programs: programs whose correctness is proved formally within the system. In our case, the program will be one that produces machine-checked proofs of hybrid system safety, obtained using the abstraction method.

@@

Both are weaker than the original, and are less straightforward to use. Nevertheless, this is the path we will take in our development, partly out of necessity (because in some parts of the development, we really need to ``run'' these lemmas to obtain |<=|/|<| proofs), and partly because just taking |le_lt_dec| as an axiom amounts to cheating.

>>>>

The prototype implementation described in \cite{alur} was developed in a conventional programming language using libraries that use ordinary floating point arithmetic \todo{which language/libraries exactly?}. The potential for bugs and floating point artifacts inherent in this approach limit the confidence one can justifiably have in safety judgements made by such an implementation. In this report, we describe a reimplementation of the basic technique in Coq, a proof assistant based on a rich type theory that also functions as a programming language, letting one develop ``certified'' programs: programs whose correctness is proved formally within the system. In our case, the program will be one that produces machine-checked proofs of hybrid system safety, obtained using the abstraction method.

@@

Both are weaker than the original, and are less straightforward to use. Nevertheless, this is the path we will take in our development, partly out of necessity (because in some parts of the development, we really need to ``run'' these lemmas to obtain |<=|/|<| proofs), and partly because just taking |le_lt_dec| as an axiom amounts to cheating. \todo{the former is a lie. paste the new perspective as written in mail to Herman, and/or stuff from our paper}
